\documentclass[a4paper,10pt]{article}

%==================== PACKAGES ====================
\usepackage[left=0.5in,right=0.5in,top=0.35in,bottom=0.35in]{geometry}
\usepackage[colorlinks=true,urlcolor=black]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{helvet}

%==================== FONT SETTINGS ====================
\renewcommand{\familydefault}{\sfdefault}

%==================== GLOBAL SETTINGS ====================
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\linespread{1.05}

\hyphenpenalty=10000
\exhyphenpenalty=10000
\sloppy

%==================== SECTION FORMATTING ====================
\titleformat{\section}
{\fontsize{11}{13}\selectfont\bfseries}
{}{0em}{}[\titlerule]

\titlespacing*{\section}{0pt}{6pt}{2pt}

\begin{document}

%==================== HEADER ====================
\begin{center}

{\fontsize{20}{22}\selectfont\textbf{PONKRISHNAN P}}\\[3pt]

{\fontsize{9.8}{11}\selectfont
\href{tel:+919894256060}{+91 9894256060}
\;$|$\;
\href{mailto:ponkrishnan4@gmail.com}{ponkrishnan4@gmail.com}
\;$|$\;
\href{https://www.linkedin.com/in/ponkrishnan-p-1316ab259/}{\underline{LinkedIn}}
\;$|$\;
\href{https://github.com/Ponkrishnan}{\underline{GitHub}}
}

\end{center}

\vspace{-3pt}

%==================== PROFESSIONAL SUMMARY ====================
\section*{PROFESSIONAL SUMMARY}

{\fontsize{10}{12.5}\selectfont
Software Engineering graduate with a strong foundation in DSA, OOP, and backend systems. Hands-on experience designing, implementing, and testing scalable, high-performance RESTful APIs using Java, Python, Spring Boot, and FastAPI. Skilled in writing unit and functional tests, building CI/CD pipelines, and using telemetry and metrics to drive operational excellence in Agile teams.
}

%==================== TECHNICAL SKILLS ====================
\section*{TECHNICAL SKILLS}

\begin{itemize}[leftmargin=0.16in,itemsep=1.5pt,topsep=2pt]

\item \textbf{Languages:} Java $\mid$ Python $\mid$ JavaScript $\mid$ C++ $\mid$ SQL

\item \textbf{Frameworks:} Spring Boot $\mid$ FastAPI $\mid$ Node.js $\mid$ React.js $\mid$ REST APIs

\item \textbf{Testing \& Tools:} JUnit $\mid$ PyTest $\mid$ Postman $\mid$ Unit \& Integration Testing $\mid$ Git $\mid$ GitHub

\item \textbf{Cloud \& DevOps:} AWS (EC2, S3) $\mid$ Docker $\mid$ CI/CD $\mid$ Linux

\item \textbf{Databases:} MySQL $\mid$ PostgreSQL $\mid$ MongoDB

\item \textbf{Core CS:} DSA $\mid$ OOP $\mid$ DBMS $\mid$ Operating Systems $\mid$ System Design $\mid$ Agile

\end{itemize}

%==================== WORK EXPERIENCE ====================
\section*{WORK EXPERIENCE}

\textbf{DarwinBox} -- Product Development Intern (Hyderabad)
\hfill Jan 2026 -- Apr 2026

\begin{itemize}[leftmargin=0.16in,itemsep=1.5pt,topsep=2pt]

\item Designed and implemented scalable RESTful APIs for enterprise HR and payroll modules using Python and FastAPI.

\item Wrote unit and integration tests, improving code coverage and reducing regression defects across production releases.

\item Optimized SQL queries and backend workflows, reducing API response time and improving overall system reliability.

\item Added logging, telemetry, and metrics dashboards to monitor service health and drive operational excellence.

\item Collaborated with engineers and QA in Agile sprints through code reviews, CI/CD pipelines, and production deployments.

\end{itemize}

%==================== PROJECTS ====================
\section*{PROJECTS}

\textbf{AutoGenX -- AI Vehicle Diagnostic Platform}
\hfill Python $\mid$ FastAPI $\mid$ React.js $\mid$ MongoDB

\begin{itemize}[leftmargin=0.16in,itemsep=1.5pt,topsep=2pt]

\item Built a scalable diagnostic platform processing real-time vehicle sensor data via low-latency REST APIs and backend services.

\item Integrated LLM-based pipelines using RAG and NLP to generate intelligent insights from structured and unstructured data.

\item Designed interactive dashboards to visualize diagnostic data and system performance metrics in real time.

\item Wrote automated tests and added logging to monitor system health and ensure release quality.

\end{itemize}

\textbf{AI Data Layer -- Enterprise HR Intelligence Platform}
\hfill Java $\mid$ Spring Boot $\mid$ PostgreSQL $\mid$ AWS

\begin{itemize}[leftmargin=0.16in,itemsep=1.5pt,topsep=2pt]

\item Designed scalable backend services to manage HR, payroll, and recruitment datasets across multi-tenant architecture.

\item Implemented secure REST APIs with Role-Based Access Control (RBAC) ensuring data isolation and enterprise-grade security.

\item Built ETL pipelines and optimized database queries to improve data processing performance and scalability.

\item Developed KPI engines for workforce analytics, enabling automated reporting and decision support.

\end{itemize}

\textbf{DriveGuard -- AI Driver Safety Monitoring System}
\hfill Python $\mid$ OpenCV $\mid$ MongoDB $\mid$ REST APIs

\begin{itemize}[leftmargin=0.16in,itemsep=1.5pt,topsep=2pt]

\item Developed a real-time driver safety system to detect fatigue, distraction, and unsafe behavior using computer vision.

\item Built backend REST APIs and event-driven services for low-latency alert generation and analytics tracking.

\item Designed MongoDB schemas to efficiently store driver behavior logs and event history for analytics.

\item Implemented automated tests and logging to validate detection accuracy and ensure production-grade reliability.

\end{itemize}

%==================== EDUCATION ====================
\section*{EDUCATION}

\textbf{B.Tech in Artificial Intelligence and Data Science}
\hfill 2022 -- 2026

Sri Eshwar College of Engineering (Affiliated to Anna University), Coimbatore
\hfill CGPA: 7.5+ \;$|$\; No Backlogs

\textbf{Relevant Coursework:} Data Structures \& Algorithms, OOP, DBMS, Operating Systems, Computer Networks, System Design, Software Engineering.

%==================== ACHIEVEMENTS & CERTIFICATIONS ====================
\section*{ACHIEVEMENTS \& CERTIFICATIONS}

\begin{itemize}[leftmargin=0.16in,itemsep=1.5pt,topsep=2pt]

\item Solved \textbf{450+ DSA problems on LeetCode}

\item \textbf{AWS Cloud Quest: Cloud Practitioner} certified -- AWS. \href{https://www.credly.com/badges/a897819a-28eb-4b6e-83cd-2d551edce741/public_url}{\underline{(Link)}}

\item \textbf{NPTEL Cloud Computing (Elite)} certification -- IIT. \href{https://drive.google.com/file/d/1AlVEIrL-f_hkd__S5qX9O9k5cE_flgpr/view}{\underline{(Link)}}

\item Java Programming \& DSA using C/C++ certifications -- Udemy. \href{https://drive.google.com/file/d/10tCBEQrc_k7DRdEFh7xHsQ77UmIKP3Ha/view}{\underline{(Link)}}

\end{itemize}

\end{document}
